\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Design Trends}
\author{Samridhi Saini}
\date{June 2022}

\begin{document}

\maketitle

\section{Introduction}
 Design is the practice of making something that’s beautiful. As a design trend, User Experience Design is one of the most significant fields in today’s information age because it helps companies create better products and services for their customers.
The top UX design trends for 2022 will focus on how we can make the web of things more personal and compelling. People are increasingly demanding customization as a feature, and from manufacturers as well as from designers of individual user experience (UX).
User experience design is essential for the success of any product. Top UX design trends of 2022: AR/VR, AI, crowdsourcing, and digital assistants
The top UX design trends of 2022 are the rise of the digital native. We'll see emerging product categories like wearables and DIY products that use smart tech to make the entire workflow more efficient. The top UX design trends of 2022 according to other source  are user interface, data security and privacy, artificial intelligence, augmented reality, and robotics.

\subsubsection{Top UX design trends of 2022}
1. Natural User Interfaces 
 The main trend for 2022 is natural user interfaces. The design should make a real connection with the user from the start and not just inform them of functions or benefits. It should be easy to grasp, provide feedback and have emotional impact.

2. Experience-based Design
 Experience-based Design is the integration of user experience design and discovery into business models and processes. This has allowed companies to focus their efforts on improving technology products by focusing on their use. 
 
3. Mobile For Every Screen 
 Mobile for every screen 2022 trends, Current and future trends in the technology arena of mobile devices, 2D and 3D displays and wireless Internet access
4. Contextual Interactions
Contextual Interactions are one of the most interesting and valuable trends in UX design. Contextual Interactions help users enter a flow state, which make them feel like they’re becoming a part or contributing to something. In short, they are hands-on and make users feel emotionally included in the action.

5. AI-enabled Software
 AI-enabled software UX ui trends in 2022 represents a more user-centric, engaging and adaptive user experience. It is expected to deliver more personalized interactions between users, organizations and technology through a more intuitive user interface that allows users to gain an understanding of their identity and skills.
 
 6. Augmented Reality
 Augmented Reality ux ui trends in 2022 to take your business past the threshold of being a user experience design trend. Augmented reality or virtual reality (augmented reality and virtual reality, respectively), is the creation of an artificial world (an immersive experience), combining elements of both the real world and the digital world. Augmented reality ux designs show a creative and effective way to replace traditional websites by allowing users to create a fully immersive experience that surpasses what is possible with a desktop computer.
 
\subsubsection{Customers as Competitors in Purchasing Decisions.} 
1. Wearable Technology
The wearable technology industry has exploded over the past few years and you can find tons of wearable devices at your local electronics store. The main purpose of these devices is to track your daily activities, including steps and sleep, heartbeat and more to help you improve your health and overall wellbeing. But there are also other different types of wearables, like exercise bands and even watch-like devices that come with impressive features like GPS tracking for for skiing or hiking.

 2. IoT-based Workshops
 This book analyzes the future trends and designs of top user experience design and user interface moving towards 2022. It also presents the IoT-based workshops and UI/UX makes. This will give you a comprehensive understanding of how technology is changing our lives, and how you can use it to create breakthroughs in your business.
 
 Customers as Competitors in Purchasing Decisions these are more of them Physical Stores, Conversational Commerce, Social Commerce, Glocalization. More Complex Interactions
 
 \section{summary}
 There are more than 1.25 billion mobile devices in use globally today, according to the U.S. Department of Commerce’s Bureau of Economic Analysis. That number is expected to grow at a rate of 8% annually over the next five years and will reach almost 2 billion by 2022 (the same year that the entire world population using Google’s search engine).  Top ux design trends of 2022 will help improve user experience, increase user adoption and increase the efficiency of a product. In addition to that top-notch ux design trends 2022 make customers fall in love with your product.The key is to stay at the forefront of these developments, because if you don't, your competitors will! Since user experience can make or break a product or service, it is vital that you are always evolving as a business .

 The rapid evolution of the user experience has brought us to a new level of user engagement. The top UX design trends for 2022 will change the way we interact with our devices and the world.


\end{document}

